### 2020-10-17 serial.tex
figure label
sig state

The generation- and serial-interval distributions are key, but different, quantities in outbreak analyses.
Recent theoretical studies suggest that the two distributions give different estimates of the reproduction number \RR as inferred from the observed exponential growth rate $r$;
however, both intervals, by definition, describe disease transmission at the individual level.
Here, we show that estimating \RR based on $r$ and the serial-interval distribution, when defined from the correct reference time and cohort, gives the same estimate as using $r$ and the generation-interval distribution.
We apply our framework to serial-interval data from the COVID-19 outbreak in China, outside Hubei province (January  21--February 8, 2020), revealing systematic biases in prior inference methods.
Our study provides the theoretical basis for practical changes to the principled use of serial interval distributions in estimating \RR during epidemics.

@@

>>>>

The generation- and serial-interval distributions are key, but different, quantities in outbreak analyses.
Recent theoretical studies suggest that the two distributions give different estimates of the reproduction number \RR as inferred from the observed exponential growth rate $r$.
Here, we show that estimating \RR based on $r$ and the serial-interval distribution, when defined from the correct reference time and cohort, gives the same estimate as using $r$ and the generation-interval distribution.
We apply our framework to serial-interval data from the COVID-19 outbreak in China, outside Hubei province (January  21--February 8, 2020), revealing systematic biases in prior inference methods.
Our study provides the theoretical basis for practical changes to the principled use of serial interval distributions in estimating \RR during epidemics.

@@

\renewcommand\thefigure{S\arabic{figure}}    
\setcounter{figure}{0}
